Turbulence in compact to giant HII regions

### 2022-11-11 strucfunc_paper.tex
Javier  changes 2022-11-11

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. García Vázquez et al.]{
J. García Vázquez$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
%J. Zsargo,$^{1}$
and W. J. Henney$^{2}$
%and H. O. Castañeda$^{1}$
\\
% List of institutions
$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México.\\
$^{2}$Instituto de Radioastronomía y Astrofísica, Universidad Nacional Autonoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
}

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2021}

@@

The archival data for the extragalactic giant regions (GEHRs), NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument
\citep{Gordon:2000v}
on the \SI{4.2}{m} William Herschel Telescope (WHT) and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
The IPCS-II detector was used with a etalon of \SI{125}{\mu m}.
Each data cube is \(256 \times 256 \times 100\) with a spatial scale of \SI{0.26}{arcsec.pixel^{-1}} with a total integration time of \SI{3600}{s} (\SI{36}{s} per frame).
For more details on the observational setup see table~1 of \citet{sabalisck1995supersonic}.
The reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L} and the emission spectrum was adjusted with a Gaussian fit.
The NGC~604 observations were previously reported and analyzed in
\citet{sabalisck1995supersonic}, \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}.

@@

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters taken from Table 2 of \citet{1984ApJ...287..116K}. Mean non-thermal linewidth values, \(\langle \sigma\los \rangle\), shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    39.01    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

\newcommand\LL{\mathcal{L}}
Slightly different definitions of the correlation length
are found in the literature.
For instance the definition of \citet{Jaupart:2022i}
in two dimensions is
\begin{equation}
  \label{eq:2}
  \ell_c^2 = \frac{1}{4} \int C(r) \, d^2 r
  = \frac{\pi}{2} \int_0^\infty r C(r) \, d r
\end{equation}
while the ``integral length scale'' \citep{Pope:2000p} is defined
as
\begin{equation}
  \label{eq:3}
  \LL \equiv \int_0^\infty C(r)\, dr .
\end{equation}
For our model structure function, these evaluate to
\begin{equation}
  \label{eq:4}
  \LL = \frac{\Gamma(1/m)}{m\, (\ln 2)^{1/m}} \, r_0
\end{equation}
and
\begin{equation}
  \label{eq:4}
   \ell_c^2 = \frac{\pi\,  \Gamma(2/m)}{2m\, (\ln 2)^{1/m}} \, r_0^2
\end{equation}
where \(\Gamma\) is the usual Gamma function.
For example, if \(m = 1\) these become \(\LL \approx 1.443 r_0\)
and \(\ell_c \approx 1.808 r_0\). 
% The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
% In an idealized case at scales larger than \(r_{0}\)\ the structure function flattens as it tends towards the asymptotic value of 2\(\sigma^2\) \citep{arthur2016turbulence}.
% This substitutes the previously \(C(r) = 1/[1+(r/r_{0})^{m}]\) from \citet{1966igd..book.....K} and
% \citet{1984ApJ...277..556S}.

@@

The posterior distributions of model parameters
that are consistent with the observations for each region are estimated
using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
A uniform prior distribution is assumed between upper and lower bounds
for each parameter, as given in Table~\ref{tab:parameter-ranges}.
To help ensure convergence of the MCMC algorithm,
we used chain lengths that exceeded \num{50} times the
estimated autocorrelation length for each parameter,
which typically required of order \num{50000} samples.
Thin translucent lines in the figures show structure functions using the parameters of
a random selection of \num{100} posterior samples from the MCMC chain,
both for \(\tilde{B}\model(r)\) orange and \(B\model(r)\) (green).
This gives an estimate in the uncertainty about the best-fit model.
Credibility intervals for the parameters are estimated from percentiles
of the posterior distribution and are indicated in the figures by shaded gray boxes
around the best-fit parameter values
(heavy shading for 68\% interval; light shading for 95\% interval).
The 95\% credibility interval for each parameter and for each source
is also given in Table~\ref{tab:Res}.
Figure~\ref{fig:corner-example-Orion} gives an example for Orion of
the pairwise correlations in the posterior distributions of the model parameters,
plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
Corresponding plots for the remaining sources and a table for the fitting parameters are given in Appendix~\ref{sec:addit-covar-corn}.

@@

In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structural functions of some \hii{} regions of our sample.
In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.

@@

The values of \(D\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
limits seen from visual inspection of \ha{} photographs.
These values would represent an upper limit of the size of each region.
Since these objects do not posses physical edges the determination of their size is not trivial.
Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.

@@

The dependence on \(r_0\) and the diameter can be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[J. García Vázquez et al.]{
J. García Vázquez$^{1}$\thanks{E-mail: jgarciav1600@alumno.ipn.mx}
and W. J. Henney$^{2}$
\\
% List of institutions
$^{1}$Escuela Superior de Física y Matemáticas, Instituto Politécnico Nacional, Ciudad de México, México.\\
$^{2}$Instituto de Radioastronomía y Astrofísica, Universidad Nacional Autonoma de México, Apartado postal 3-72, 58090 Morelia, Michoacán, Mexico\\
}

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2023}

@@

The archival data for the extragalactic giant regions (GEHRs), NGC 604, NGC 595, Hubble X and Hubble V was obtained with the Fabry Perot TAURUS-II instrument
\citep{Gordon:2000v}
on the \SI{4.2}{m} William Herschel Telescope (WHT) and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}.
The IPCS-II detector was used with a etalon of \SI{125}{\mu m}.
Each data cube is \(256 \times 256 \times 100\) with a spatial scale of \SI{0.26}{arcsec.pixel^{-1}} with a total integration time of \SI{3600}{s} (\SI{36}{s} per frame).
For more details on the observational setup see table~1 of \citet{sabalisck1995supersonic}.
The reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L} and the emission spectrum was adjusted with a single Gaussian fit.
The NGC~604 observations were previously reported and analyzed in
\citet{sabalisck1995supersonic}, \citet{Medina-Tanco:1997a} and \citet{Melnick:2021x}.

@@

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Diameters taken from Table 2 of \citet{1984ApJ...287..116K}. Mean non-thermal linewidth values (\(\langle \sigma\los \rangle\)) shown here are corrected considering equation \eqref{eq:sigma-los} which takes into account \(\sigma_{\mathrm{fs}}\). Non-corrected \(\langle \sigma\los \rangle\) values and other properties references are mentioned in the text. }
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d & \text{Diameter,}\ D_{\hii} & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.44 \pm 0.02  & 5 \pm 0.5    &    37.18       &    9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.2 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    39.01    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &     21.7 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &    9.6 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.0 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &    9.8 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.5 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.5 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

@@

\newcommand\LL{\mathcal{L}}
Slightly different definitions of the correlation length
are found in the literature.
For instance the definition of \citet{Jaupart:2022i}
in two dimensions is
\begin{equation}
  \label{eq:2}
  \ell_c^2 = \frac{1}{4} \int C(r) \, d^2 r
  = \frac{\pi}{2} \int_0^\infty r C(r) \, d r
\end{equation}
while the ``integral length scale'' \citep{Pope:2000p} is defined
as
\begin{equation}
  \label{eq:3}
  \LL \equiv \int_0^\infty C(r)\, dr .
\end{equation}
For our model structure function, these evaluate to
\begin{equation}
  \label{eq:4}
  \LL = \frac{\Gamma(1/m)}{m\, (\ln 2)^{1/m}} \, r_0
\end{equation}
and
\begin{equation}
  \label{eq:4}
   \ell_c^2 = \frac{\pi\,  \Gamma(2/m)}{2m\, (\ln 2)^{2/m}} \, r_0^2
\end{equation}
where \(\Gamma\) is the usual Gamma function.
For example, if \(m = 1\) these become \(\LL \approx 1.443 r_0\)
and \(\ell_c \approx 1.808 r_0\). 
% The term \(r_{0}\)\ is the correlation length where the value of separation \(r\) reach the value of \(\sigma^2\) in the structure function and $m$ is the power-law index that fits the inertial scale.
% In an idealized case at scales larger than \(r_{0}\)\ the structure function flattens as it tends towards the asymptotic value of 2\(\sigma^2\) \citep{arthur2016turbulence}.
% This substitutes the previously \(C(r) = 1/[1+(r/r_{0})^{m}]\) from \citet{1966igd..book.....K} and
% \citet{1984ApJ...277..556S}.

@@

The posterior distributions of model parameters
that are consistent with the observations for each region are estimated
using Markov Chain Monte Carlo (MCMC) ensemble sampling \citep{2010CAMCS...5...65G}
as implemented in the \texttt{emcee} Python library \citep{2013PASP..125..306F}.
A uniform prior distribution is assumed between upper and lower bounds
for each parameter, as given in Table~\ref{tab:parameter-ranges}.
To help ensure convergence of the MCMC algorithm,
we used chain lengths that exceeded \num{50} times the
estimated autocorrelation length for each parameter,
which typically required of order \num{50000} samples.
Thin translucent lines in the figures show structure functions using the parameters of
a random selection of \num{100} posterior samples from the MCMC chain,
both for \(\tilde{B}\model(r)\) (orange) and \(B\model(r)\) (green).
This gives an estimate in the uncertainty about the best-fit model.
Credibility intervals for the parameters are estimated from percentiles
of the posterior distribution and are indicated in the figures by shaded gray boxes
around the best-fit parameter values
(heavy shading for 68\% interval; light shading for 95\% interval).
The 95\% credibility interval for each parameter and for each source
is also given in Table~\ref{tab:Res}.
Figure~\ref{fig:corner-example-Orion} gives an example for Orion of
the pairwise correlations in the posterior distributions of the model parameters,
plotted using the \texttt{corner} Python library \citep{2017ascl.soft02002F}.
Corresponding plots for the remaining sources and a table for the fitting parameters are given in Appendix~\ref{sec:addit-covar-corn}.

@@

In the section \ref{sec:comp-with-prev} we make a comparison of our methods and results with previous research that analyzes structure functions of some \hii{} regions of our sample.
In the section \ref{sec:scaling-relations} we present the most important scaling relations between the derived turbulent parameters and the physical properties of the \hii{} regions.
Finally, in the section \ref{power-law-index} we discuss the role of the derived power-law index in the context of turbulence in the ionized gas.

@@

The values of \(D_{\hii}\) are taken from \citet{1984ApJ...287..116K} and correspond to the outer
limits seen from visual inspection of \ha{} photographs.
These values would represent an upper limit of the size of each region.
Since these objects do not posses physical edges the determination of their size is not trivial.
Due to the above, we chose these set values since they are from an unique source and are foreign to our calculations and observations, which reduced the bias in the scaling law we obtain.

@@

%The dependence on \(r_0\) and the diameter may be interpreted in terms that each region presents a characteristic energy injection mechanism (or combination) and despite the presence of the different mechanisms there is some unique combination that drives the input energy in each region.
